How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2020-12-14 analysis/paper/paper.Rmd
map is showing in HTML output now

```{r korea-map, fig.cap="Korean Paleolithic sites mentioned in the text.", include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/001-draw-the-map.R"))}
quietly(source(here::here("analysis/paper/001-draw-the-map.R")))
knitr::include_graphics(here::here("analysis/figures/001-site-map.png"))

>>>>

```{r korea-map, fig.cap="Korean Paleolithic sites mentioned in the text.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/001-draw-the-map.R"))}
quietly(source(here::here("analysis/paper/001-draw-the-map.R")))
knitr::include_graphics(here::here("analysis/figures/001-site-map.png"))
